Title

### 2024-05-13 paper/main.tex
udpates

\begin{abstract}
	\emph{Causal Discovery} involves learning causal structures
	from data, typically represented as  Directed Acyclic Graphs
	(DAGs) or Structural Equation Models (SEMs). This problem has been
	extensively studied for both DAGs and SEMs. In the field of DAGs, many
	automated algorithms have been developed for constructing a DAG from a
	given dataset. However, the adaption of these algorithms in applied
	fields have been limited, possibly due to a lack of confidence in these
	algorithms stemming from them making obvious mistakes, and the
	difficulties in choosing the right algorithm for a given dataset.
	Consequently, in applied disciplines, these DAGs are predominantly
	constructed manually based on domain expertise. Due to being
	constructed by hand, it is vital that the fit of these models are
	tested against data and the models are potentially modified to acheive
	a better fit. On the other hand, in the field of SEMs models are
	typically constructed manually through an iterative process of
	assessing fit and modifying the model according to that. This process
	is commonly known as \emph{Specification Search} where methods like
	\emph{modification indices} can be used to guide this modification
	process. In the case of DAGs, although there are tests such as Shipley
	2000 that can assess the global fit of model by combining the tests
	using implied conditional independencies of the model, but there are no
	methods that can guide our modification process. In this paper, we
	present a simple modification process aimed at helping researchers in
	manually constructing or modifying the DAGs outputted by an algorithm.
	This modification process is based on using a measure of association
	for these individual local CI tests to identify the worst offending CI
	test and combining it with expert knowledge. We also present a measure
	of association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}

@@

In the field of Structural Equation Models (SEMs)
modification indices have been used to do this. However, as modification index
is an evaluation of the global fit of the model. An alternative is local fit of
models using CI tests where the implied conditional independences of the model
can be tested using statistical tests. Similar to modification indices, these
tests can then be used to modify our models. Figure shows an example of this
testing. We can not also only rely on the p-values, effect size can help in
deciding.

\textbf{Para 4: Measure of Association}
As these CI based testing uses p-values and effect size measures from CI tests
for testing. And as mixed data is common, we need both a test and effect size
measure for mixed data. Recently, a few CI tests for mixed data have been
proposed but an effect size is still missing.

>>>>

\begin{abstract}
	\emph{Causal Discovery} involves learning causal structures
	from data, and has been studied both in Directed Acyclic Graphs
	(DAGs) and Structural Equation Models (SEMs). This problem has been
	extensively studied for both DAGs and SEMs. In the field of DAGs, many
	automated algorithms have been developed for constructing a DAG from a
	given dataset. However, the adaption of these algorithms in applied
	fields have been limited, possibly due to a lack of confidence in these
	algorithms stemming from them making obvious mistakes, and the
	difficulties in choosing the right algorithm for a given dataset.
	Consequently, in applied disciplines, these DAGs are predominantly
	constructed manually based on domain expertise. Due to being
	constructed by hand, it is vital that the fit of these models are
	tested against data and the models are potentially modified to acheive
	a better fit. On the other hand, in the field of SEMs models are
	typically constructed manually through an iterative process of
	assessing fit and modifying the model according to that. This process
	is commonly known as \emph{Specification Search} where methods like
	\emph{modification indices} can be used to guide this modification
	process. In the case of DAGs, although there are tests such as Shipley
	2000 that can assess the global fit of model by combining the tests
	using implied conditional independencies of the model, but there are no
	methods that can guide our modification process. In this paper, we
	present a simple modification process aimed at helping researchers in
	manually constructing or modifying the DAGs outputted by an algorithm.
	This modification process is based on using a measure of association
	for these individual local CI tests to identify the worst offending CI
	test and combining it with expert knowledge. We also present a measure
	of association based on canonical correlations for mixed data. We also
	present a graphical web-tool that can assist researchers in iteratively
	modifying and constructing their DAGs. We theoretically show that in
	the presence of an oracle, this iterative modification process is
	consistent in recovering the true DAG. Emprically, we show that this
	process performs comparably to PC and Hill-Climb Search algorithms if
	the user is able to correctly identify the direction of the edge in one
	out of three cases.
\end{abstract}

@@

In the field of Structural Equation Models (SEMs), models are typically
constructed by hand. Researchers typically come up with an initial model, which
then they use the data to make modifications to. This process is known as
\emph{Specification Search}. One of the common ways to do this is through
\emph{modification indices} where a global fit of the model is measured with
different modification to the model. Utilizing expert knowledge to select the
appropriate modification that gives the maximum improvement to the global fit.

% modification indices have been used to do this. However, as modification index
% is an evaluation of the global fit of the model. An alternative is local fit of
% models using CI tests where the implied conditional independences of the model
% can be tested using statistical tests. Similar to modification indices, these
% tests can then be used to modify our models. Figure shows an example of this
% testing. We can not also only rely on the p-values, effect size can help in
% deciding.

\textbf{Para 4: Measure of Association}
In the case of DAGs however, we do not have any way to 
As these CI based testing uses p-values and effect size measures from CI tests
for testing. And as mixed data is common, we need both a test and effect size
measure for mixed data. Recently, a few CI tests for mixed data have been
proposed but an effect size is still missing.
